Parameter Inference\\with Bifurcation Diagrams

### 2021-05-27 docs/article.tex
update article

% something here about how this helps high-level design of dynamical systems and is useful to the wider scientific machine learning community

>>>>

In dynamical systems theory the geometry of state-space determines all of the qualitative behaviours of a system. Our work makes progress towards designing models directly in state-space, rather than the spatial or temporal domain. This is valuable to experimentalists who only have qualitative observations available to them and wish to navigate the space of qualitative behaviours of their system. Our work lies within a trend of progress in the scientific machine learning community, where structured domain-informed models are favoured over flexible models that live in large parameter spaces.
